```{r, include = FALSE}
# snakemake <- readRDS(".correlation.Rmd.RDS")
snakemake@source("R/rmd_setup.R")

library(data.table)
library(dplyr)
library(ggplot2)
library(foreach)
library(ggpubr)

config <- snakemake@config

samples <- fread(snakemake@input$samples) %>%
  .[ , Region := gsub(Region, pattern = "_", replacement = " ") ] %>%
  .[ , Region := gsub(Region, pattern = "23", replacement = "2/3") ] %>%
  .[ , Layer := gsub(Layer, pattern = "23", replacement = "2/3") ]

corr <- foreach(file = snakemake@input$correlation, .combine = cbind, .inorder = TRUE) %do% {
  corr <- fread(file)
  apply(corr, 2, mean)
}

sids <- foreach(file = snakemake@input$correlation, .combine = c, .inorder = TRUE) %do% {
  gsub(file, pattern = ".*(W./C.*)/lagged_correlation.csv", replacement = "\\1") %>%
    gsub(pattern = "/", replacement = "_")
}

colnames(corr) <- sids

time <- seq(-20000, 20000 - 50, by = 50) / 20000

dt <- corr %>%
  reshape2::melt() %>%
  as.data.table() %>%
  setnames(c("ID", "SID", "Correlation")) %>%
  .[ , Time := rep(time, times = length(unique(SID))) ] %>%
  .[ , MaxCorrelation := max(abs(Correlation)), by = SID ] %>%
  merge(samples, by = "SID")
```

---
date: <small>`r Sys.Date()`</small>
author: <small>`r config$report$author`</small>
title: `r config$report$title`
---

# Membrane potential and EMG correlation

## Lagged correlations

```{r, include = TRUE, fig.height = 5.4}
plots <- foreach(region = dt[ , unique(Region) ] %>% sort()) %do% {
  dt[ Region == region ] %>%
    ggplot() +
    facet_grid(~Region) +
    geom_line(aes(x = Time, y = Correlation, group = SID), linewidth = 0.25, color = "gray") +
    geom_line(data = dt[ Region == region, list(Correlation = mean(Correlation)), by = Time ],
              aes(x = Time, y = Correlation), linewidth = 0.5, color = "black") +
    theme_light(base_size = 8) +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    expand_limits(y = c(-0.1, 0.5))
}

ggarrange(
  plotlist = plots,
  labels = letters[ 1:4 ],
  font.label = list(size = 9)
)
```

**Figure 1.** Average membrane potential and EMG recording correlations in individual recordings (gray) and
all recordings from the same area (black).

```{r, include = TRUE, fig.height = 2.8}
# TODO: insert test for offset from zero!

p1 <- dt[ ,
  list(Correlation = mean(Correlation)),
  by = list(Time, Region)
] %>%
  ggplot() +
  geom_line(aes(x = Time, y = Correlation, color = Region), linewidth = 0.5) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))

p2 <- dt[ ,
  list(Correlation = mean(Correlation)),
  by = list(Time, Layer)
] %>%
  ggplot() +
  geom_line(aes(x = Time, y = Correlation, color = Layer), linewidth = 0.5) +
  theme_light(base_size = 8) +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  theme(legend.position = "top")

p3 <- dt[ ,
  list(Correlation = mean(Correlation)),
  by = list(Time, Cortex)
] %>%
  ggplot() +
  geom_line(aes(x = Time, y = Correlation, color = Cortex), linewidth = 0.5) +
  theme_light(base_size = 8) +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  theme(legend.position = "top")

ggarrange(
  p1, p2, p3,
  nrow = 1,
  labels = letters[ 1:3 ],
  font.label = list(size = 9)
)
```

**Figure 2.** Average membrane potential and EMG recording correlations in all regions **(a)**,
different layers **(b)**, and different cortices **(c)**.

<br>
<br>

## Correlation peak time

```{r, include = TRUE, warning = FALSE, fig.height = 2.8}
p1 <- dt %>%
  .[ Correlation == MaxCorrelation ] %>%
  ggplot(aes(x = Region, y = Time)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(size = 0.5, alpha = 0.5, color = "black", height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(
      c("M1 L2/3", "M1 L5"),
      c("S1 L2/3", "S1 L5"),
      c("M1 L2/3", "S1 L2/3"),
      c("M1 L2/3", "S1 L5"),
      c("M1 L5", "S1 L2/3"),
      c("M1 L5", "S1 L5")
    ),
    size = 2.5
  ) +
  theme_light(base_size = 8) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

p2 <- dt %>%
  .[ Correlation == MaxCorrelation ] %>%
  ggplot(aes(x = Layer, y = Time)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(aes(color = Cortex), size = 1, height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(c("L2/3", "L5")),
    size = 2.5,
    method = "wilcox.test"
  ) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

p3 <- dt %>%
  .[ Correlation == MaxCorrelation ] %>%
  ggplot(aes(x = Cortex, y = Time)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(aes(color = Layer), size = 1, height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(c("M1", "S1")),
    size = 2.5,
    method = "wilcox.test"
  ) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

ggarrange(
  p1, p2, p3,
  nrow = 1,
  labels = letters[ 1:3 ],
  font.label = list(size = 9),
  widths = c(0.5, 0.25, 0.25)
)
```

**Figure 3.** Correlation peak time in all regions **(a)**, different layers **(b)**, and
different cortices **(c)**.

<br>
<br>

## Maximum correlation

```{r, include = TRUE, warning = FALSE, fig.height = 2.8}
p1 <- dt %>%
  .[ Correlation == MaxCorrelation ] %>%
  ggplot(aes(x = Region, y = Correlation)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(size = 0.5, alpha = 0.5, color = "black", height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(
      c("M1 L2/3", "M1 L5"),
      c("S1 L2/3", "S1 L5"),
      c("M1 L2/3", "S1 L2/3"),
      c("M1 L2/3", "S1 L5"),
      c("M1 L5", "S1 L2/3"),
      c("M1 L5", "S1 L5")
    ),
    size = 2.5
  ) +
  theme_light(base_size = 8) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

p2 <- dt %>%
  .[ Correlation == MaxCorrelation ] %>%
  ggplot(aes(x = Layer, y = Correlation)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(aes(color = Cortex), size = 1, height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(c("L2/3", "L5")),
    size = 2.5,
    method = "wilcox.test"
  ) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

p3 <- dt %>%
  .[ Correlation == MaxCorrelation ] %>%
  ggplot(aes(x = Cortex, y = Correlation)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(aes(color = Layer), size = 1, height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(c("M1", "S1")),
    size = 2.5,
    method = "wilcox.test"
  ) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

ggarrange(
  p1, p2, p3,
  nrow = 1,
  labels = letters[ 1:3 ],
  font.label = list(size = 9),
  widths = c(0.5, 0.25, 0.25)
)
```

**Figure 4.** Correlation peak time in all regions **(a)**, different layers **(b)**, and
different cortices **(c)**.

<br>
<br>

## Non-lagged correlation

```{r, include = TRUE, warning = FALSE, fig.height = 2.8}
p1 <- dt %>%
  .[ Time == 0 ] %>%
  ggplot(aes(x = Region, y = Correlation)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(size = 0.5, alpha = 0.5, color = "black", height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(
      c("M1 L2/3", "M1 L5"),
      c("S1 L2/3", "S1 L5"),
      c("M1 L2/3", "S1 L2/3"),
      c("M1 L2/3", "S1 L5"),
      c("M1 L5", "S1 L2/3"),
      c("M1 L5", "S1 L5")
    ),
    size = 2.5
  ) +
  theme_light(base_size = 8) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

p2 <- dt %>%
  .[ Time == 0 ] %>%
  ggplot(aes(x = Layer, y = Correlation)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(aes(color = Cortex), size = 1, height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(c("L2/3", "L5")),
    size = 2.5,
    method = "wilcox.test"
  ) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

p3 <- dt %>%
  .[ Time == 0 ] %>%
  ggplot(aes(x = Cortex, y = Correlation)) +
  geom_boxplot(linewidth = 0.25, outlier.alpha = 0) +
  geom_jitter(aes(color = Layer), size = 1, height = 0, width = 0.25) +
  stat_compare_means(
    comparisons = list(c("M1", "S1")),
    size = 2.5,
    method = "wilcox.test"
  ) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(legend.margin = margin(0, 0, 0, 0)) +
  theme(legend.box.margin = margin(-5, 0, -5, 0)) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

ggarrange(
  p1, p2, p3,
  nrow = 1,
  labels = letters[ 1:3 ],
  font.label = list(size = 9),
  widths = c(0.5, 0.25, 0.25)
)
```

**Figure 5.** Correlation at 0 time point in all regions **(a)**, different layers **(b)**, and
different cortices **(c)**.
