```{r r_setup, include = FALSE}
# snakemake <- readRDS(".final_emg_episodes.Rmd.RDS")
snakemake@source("R/rmd_setup.R")
snakemake@source("R/getSampleFile.R")
library(data.table)
library(dplyr)
library(foreach)
library(ggplot2)

config <- snakemake@config

samples <- fread(snakemake@input$samples)


```

---
date: <small>`r Sys.Date()`</small>
author: <small>`r config$report$author`</small>
title: `r config$report$title`
---

# Filtering detected episodes

The detected movement and rest episodes were filtered and only the episodes longer than 500 ms were kept for further analysis. The movement episodes were also required to follow a rest period of at least 500 ms.

```{r}
all <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]

  movement <- fread(getSampleFile(snakemake@input$movement, sample[ , AnimalID ], sample[ , CellName ]))
  rest <- fread(getSampleFile(snakemake@input$rest, sample[ , AnimalID ], sample[ , CellName ]))

  rbind(movement, rest) %>%
    .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}

filter <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]

  movement <- fread(getSampleFile(snakemake@input$movement_filter, sample[ , AnimalID ], sample[ , CellName ]))
  rest <- fread(getSampleFile(snakemake@input$rest_filter, sample[ , AnimalID ], sample[ , CellName ]))

  rbind(movement, rest) %>%
          .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}
```

```{r, include = TRUE}
rbind(
  all[ Movement == TRUE, list(Count = .N, Type = "Before"), by = SID ],
  filter[ Movement == TRUE, list(Count = .N, Type = "After"), by = SID ]
) %>%
  .[ , Type := factor(Type, levels = c("Before", "After")) ] %>%
  ggplot() +
  geom_bar(aes(x = SID, y = Count, fill = Type), stat = "identity", position = "dodge") +
  theme_light(base_size = 8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab("") +
  theme(legend.position = "top") +
  theme(legend.title = element_blank())
```

**Figure 1.** Number of detected movement episodes before and after filtering.

```{r, include = TRUE}
rbind(
  all[ Movement == FALSE, list(Count = .N, Type = "Before"), by = SID ],
  filter[ Movement == FALSE, list(Count = .N, Type = "After"), by = SID ]
) %>%
  .[ , Type := factor(Type, levels = c("Before", "After")) ] %>%
  ggplot() +
  geom_bar(aes(x = SID, y = Count, fill = Type), stat = "identity", position = "dodge") +
  theme_light(base_size = 8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab("") +
  theme(legend.position = "top") +
  theme(legend.title = element_blank())
```

**Figure 2.** Number of detected rest episodes before and after filtering.
