```{r, include = FALSE}
# snakemake <- readRDS(".movement_vs_rest.Rmd.RDS")
snakemake@source("R/rmd_setup.R")
snakemake@source("R/getSampleFile.R")
library(data.table)
library(dplyr)
library(foreach)
library(ggplot2)
library(ggpubr)
library(lme4)
library(lmerTest)
library(scales)

config <- snakemake@config

samples <- fread(snakemake@input$samples) %>%
  .[ , Count := NULL ] %>%
  .[ , Region := gsub(Region, pattern = "_", replacement = " ") ] %>%
  .[ , Region := gsub(Region, pattern = "23", replacement = "2/3") ] %>%
  .[ , Layer := gsub(Layer, pattern = "23", replacement = "2/3") ]

movement <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  fread(getSampleFile(snakemake@input$movement, sample[ , AnimalID ], sample[ , CellName ])) %>%
    .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}

rest <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  fread(getSampleFile(snakemake@input$rest, sample[ , AnimalID ], sample[ , CellName ])) %>%
          .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}

ap <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  fread(getSampleFile(snakemake@input$action_potentials, sample[ , AnimalID ], sample[ , CellName ])) %>%
          .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}

stats <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  fread(getSampleFile(snakemake@input$statistics, sample[ , AnimalID ], sample[ , CellName ])) %>%
          .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
} %>%
  merge(samples, by = "SID") %>%
  merge(rbind(movement, rest), by = c("ID", "SID")) %>%
  .[ , Start := Channel * 10 + Start ] %>%
  .[ , End := Channel * 10 + End ] %>%
  .[ , Episode := ifelse(Movement, "Movement", "Rest") %>% factor() ] %>%
  .[ , SID := factor(SID) ] %>%
  .[ , NumberOfAP := NumberOfAP / Length ]

stopifnot(all(samples[ , SID ] %in% movement[ , unique(SID) ]))
stopifnot(all(movement[ , unique(SID) ] %in% samples[ , SID ]))

stopifnot(all(samples[ , SID ] %in% rest[ , unique(SID) ]))
stopifnot(all(rest[ , unique(SID) ] %in% samples[ , SID ]))

# The opposite is not always true as some samples do not have
# any action potentials
stopifnot(all(ap[ , unique(SID) ] %in% samples[ , SID ]))

stopifnot(all(samples[ , SID ] %in% stats[ , unique(SID) ]))
stopifnot(all(stats[ , unique(SID) ] %in% samples[ , SID ]))
```

```{r}
plot_statistics <- function(
  data,
  variable,
  title
) {
  p1 <- data %>%
    ggpaired(x = "Episode", y = variable, id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_compare_means(comparisons = list(c("Movement", "Rest")), paired = TRUE, size = 2.5) +
    xlab("") +
    ylab(title) +
    theme_light(base_size = 8) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  p2 <- data %>%
    ggpaired(x = "Episode", y = variable, id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    facet_grid(~Region) +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_compare_means(comparisons = list(c("Movement", "Rest")), paired = TRUE, size = 2.5) +
    theme_light(base_size = 8) +
    xlab("") +
    ylab(title) +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  p3 <- data %>%
    ggpaired(x = "Episode", y = variable, id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    facet_grid(~Layer) +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_compare_means(comparisons = list(c("Movement", "Rest")), paired = TRUE, size = 2.5) +
    theme_light(base_size = 8) +
    xlab("") +
    ylab(title) +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  p4 <- data %>%
    ggpaired(x = "Episode", y = variable, id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    facet_grid(~Cortex) +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_compare_means(comparisons = list(c("Movement", "Rest")), paired = TRUE, size = 2.5) +
    theme_light(base_size = 8) +
    xlab("") +
    ylab(title) +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  ggarrange(
    ggarrange(p1, p2, widths = c(0.3, 0.7), labels = letters[ 1:2 ], font.label = list(size = 10)),
    ggarrange(p3, p4, labels = letters[ 3:4 ], font.label = list(size = 10)),
    nrow = 2
  )
}

fitModel <- function(data) {
  model.full <- lme4::lmer(
    variable ~ Episode + Start + Length + (1 + Episode | SID),
    data = data, REML = TRUE
  )

  model.null <- lme4::lmer(
    variable ~ Start + Length + (1 + Episode | SID),
    data = data, REML = TRUE
  )

  list(
    p.value = anova(model.full, model.null)$`Pr(>Chisq)`[ 2 ],
    estimate = model.full %>%
      summary() %>%
      coef() %>%
      as.data.table(keep.rownames = "FixedEffect") %>%
      .[ FixedEffect == "EpisodeRest", Estimate ]
  )
}

evaluateSignificance <- function(data, variable, compare = c("Layer", "Cortex", "Region", "All")) {
  data <- copy(data)
  data <- setnames(data, variable, "variable")

  data <- switch(
    compare,
    "Layer" = {
      data[ , list(SID, Layer, variable, Episode, Start, Length) ] %>%
        setnames("Layer", "Region")
    },
    "Cortex" = {
      data[ , list(SID, Cortex, variable, Episode, Start, Length) ] %>%
        setnames("Cortex", "Region")
    },
    "Region" = {
      data[ , list(SID, Region, variable, Episode, Start, Length) ]
    },
    "All" = {
      data[ , list(SID, Region, variable, Episode, Start, Length) ] %>%
        .[ , Region := "All" ]
    }
  )

  foreach(region = data[ , unique(Region) ], .combine = rbind) %do% {
    dt <- data[ Region == region ]
    fit <- fitModel(dt)

    dt <- dt[ , list(variable = mean(variable), Region), by = list(SID, Episode) ]

    data.table(
      Region = region,
      group1 = "Movement",
      group2 = "Rest",
      p = ifelse(fit$p.value < 0.001, scientific(fit$p.value), round(fit$p.value, 3)),
      estimate = fit$estimate,
      y.position = dt[ , max(variable) ] + dt[ , abs(max(variable)) ] * 0.1
    )
  } %>%
    .[ , y.position := max(y.position) ] %>%
    setnames("Region", compare) %>%
    .[ ]
}

plot_statistics_fit <- function(
  data,
  variable,
  title
) {
  fitAll <- evaluateSignificance(data, variable, "All")
  fitLayer <- evaluateSignificance(data, variable, "Layer")
  fitCortex <- evaluateSignificance(data, variable, "Cortex")
  fitRegion <- evaluateSignificance(data, variable, "Region")

  data <- data %>%
    copy() %>%
    setnames(variable, "variable") %>%
    .[ , list(variable = mean(variable), Cortex, Layer, Region), by = list(SID, Episode) ] %>%
    unique()

  p1 <- data %>%
    ggpaired(x = "Episode", y = "variable", id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_pvalue_manual(fitAll, size = 2.5) +
    xlab("") +
    ylab(title) +
    theme_light(base_size = 8) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  p2 <- data %>%
    ggpaired(x = "Episode", y = "variable", id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    facet_grid(~Region) +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_pvalue_manual(fitRegion, size = 2.5) +
    theme_light(base_size = 8) +
    xlab("") +
    ylab(title) +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  p3 <- data %>%
    ggpaired(x = "Episode", y = "variable", id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    facet_grid(~Layer) +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_pvalue_manual(fitLayer, size = 2.5) +
    theme_light(base_size = 8) +
    xlab("") +
    ylab(title) +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  p4 <- data %>%
    ggpaired(x = "Episode", y = "variable", id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    facet_grid(~Cortex) +
    geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(alpha = 0.5, size = 1) +
    stat_pvalue_manual(fitCortex, size = 2.5) +
    theme_light(base_size = 8) +
    xlab("") +
    ylab(title) +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

  ggarrange(
    ggarrange(p1, p2, widths = c(0.3, 0.7), labels = letters[ 1:2 ], font.label = list(size = 10)),
    ggarrange(p3, p4, labels = letters[ 3:4 ], font.label = list(size = 10)),
    nrow = 2
  )
}
```

---
date: <small>`r Sys.Date()`</small>
author: <small>`r config$report$author`</small>
title: `r config$report$title`
---

# Movement vs Rest {.tabset .tabset-pills}

**Table 1.** Average number of detected movement and rest episodes.

```{r, include = TRUE}
counts <- rbind(
  movement[ , list(Count = .N, Trials = max(Channel), Episode = "Movement", Time = sum(Length)), by = SID ],
  rest[ , list(Count = .N, Trials = max(Channel), Episode = "Rest", Time = sum(Length)), by = SID ]
) %>% merge(samples, by = "SID")

stopifnot(all(counts[ Episode == "Movement", SID ] %in% samples[ , SID ]))
stopifnot(all(counts[ Episode == "Rest", SID ] %in% samples[ , SID ]))

counts[ , list(Mean = round(mean(Count)), SD = round(sd(Count))), by = Episode ] %>%
  showTable()
```

```{r, include = TRUE, fig.height = 3.2}
averageTime <- rbind(movement, rest) %>%
  .[ , Episode := ifelse(Movement == TRUE, "Movement", "Rest") ] %>%
  .[ , list(AverageTime = mean(Length)), by = list(SID, Episode) ] %>%
  merge(samples, by = "SID")

p1 <- averageTime %>%
  ggplot(aes(x = Layer, y = AverageTime)) +
  facet_grid(~Episode) +
  geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
  geom_point(alpha = 0.5, size = 1) +
  xlab("") +
  ylab("Average length, ms") +
  stat_compare_means(comparisons = list(c("L2/3", "L5")), size = 2.5, method = "t") +
  theme_light(base_size = 8) +
  theme(strip.background = element_rect(fill = "white")) +
  theme(strip.text = element_text(colour = "black")) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

p2 <- averageTime %>%
  ggplot(aes(x = Cortex, y = AverageTime)) +
  facet_grid(~Episode) +
  geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
  geom_point(alpha = 0.5, size = 1) +
  xlab("") +
  ylab("Average length, ms") +
  stat_compare_means(comparisons = list(c("M1", "S1")), size = 2.5, method = "t") +
  theme_light(base_size = 8) +
  theme(strip.background = element_rect(fill = "white")) +
  theme(strip.text = element_text(colour = "black")) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)))

totalTime <- counts[ , list(TotalTime = max(Trials) * 10), by = SID ]

timeEval <- counts %>%
  merge(totalTime, by = "SID") %>%
  .[ , list(SID, TimeFraction = Time / TotalTime, Episode, Layer, Cortex) ]

p3 <- timeEval %>%
  ggplot(aes(x = Layer, y = TimeFraction * 100)) +
  facet_grid(~Episode) +
  geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
  geom_point(alpha = 0.5, size = 1) +
  xlab("") +
  ylab("Fraction of time, %") +
  stat_compare_means(comparisons = list(c("L2/3", "L5")), size = 2.5, method = "t") +
  theme_light(base_size = 8) +
  theme(strip.background = element_rect(fill = "white")) +
  theme(strip.text = element_text(colour = "black")) +
  scale_y_continuous(limits = c(0, 100), expand = expansion(mult = c(0.1, 0.1)))

p4 <- timeEval %>%
  ggplot(aes(x = Cortex, y = TimeFraction * 100)) +
  facet_grid(~Episode) +
  geom_boxplot(outlier.alpha = 0, fill = NA, linewidth = 0.25) +
  geom_point(alpha = 0.5, size = 1) +
  xlab("") +
  ylab("Fraction of time, %") +
  stat_compare_means(comparisons = list(c("M1", "S1")), size = 2.5, method = "t") +
  theme_light(base_size = 8) +
  theme(strip.background = element_rect(fill = "white")) +
  theme(strip.text = element_text(colour = "black")) +
  scale_y_continuous(limits = c(0, 100), expand = expansion(mult = c(0.1, 0.1)))

ggarrange(
  p1, p2, p3, p4,
  nrow = 1,
  labels = letters[1:4],
  font.label = list(size = 10)
)
```

Statistics of detected movement and rest episodes: average episode length, comparing (a) layers and (b) cortices, and the fraction of time spent in each condition, comparing (c) layers and (d) cortices. The differences between group means were evaluated using t-test.

## Episode counts {.unnumbered .unlisted}

```{r, include = TRUE, warning = FALSE, fig.height = 5.4}
plot_statistics(
  data = counts,
  variable = "Count",
  title = "Number of episodes"
)
```

**Figure 1.** Total number of detected movement and rest episodes in all samples **(a)**
and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.


## Total episode length {.unnumbered .unlisted}

```{r, include = TRUE, fig.height = 5.4}
counts <- rbind(
  movement[ , list(Count = sum(Length), Episode = "Movement"), by = SID ],
  rest[ , list(Count = sum(Length), Episode = "Rest"), by = SID ]
) %>%
  merge(samples, by = "SID")

stopifnot(all(counts[ Episode == "Movement", SID ] %in% samples[ , SID ]))
stopifnot(all(counts[ Episode == "Rest", SID ] %in% samples[ , SID ]))

plot_statistics(
  data = counts,
  variable = "Count",
  title = "Total episode length, s"
)
```

**Figure 2.** Total amount of time spent in movement and rest in all samples **(a)**
and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.


## Average episode length {.unnumbered .unlisted}

```{r, include = TRUE, warning = FALSE, fig.height = 5.4}
counts <- rbind(
  movement[ , list(Count = mean(Length), Episode = "Movement"), by = SID ],
  rest[ , list(Count = mean(Length), Episode = "Rest"), by = SID ]
) %>%
  merge(samples, by = "SID")

stopifnot(all(counts[ Episode == "Movement", SID ] %in% samples[ , SID ]))
stopifnot(all(counts[ Episode == "Rest", SID ] %in% samples[ , SID ]))

plot_statistics(
  data = counts,
  variable = "Count",
  title = "Average episode length, s"
)
```

**Figure 3.** Average amount of time spent in movement and rest in all samples **(a)**
and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.


## Episode length distribution {.unlisted .unnumbered}

```{r, include = TRUE, warning = FALSE, fig.height = 5.6}
counts <- rbind(movement, rest) %>%
  .[ , Episode := ifelse(Movement == TRUE, "Movement", "Rest") ] %>%
  merge(samples, by = "SID")

stopifnot(all(counts[ Episode == "Movement", SID ] %in% samples[ , SID ]))
stopifnot(all(counts[ Episode == "Rest", SID ] %in% samples[ , SID ]))

p1 <- counts %>%
  ggplot(aes(x = log10(Length), color = Episode, fill = Episode)) +
  geom_density(alpha = 0.25) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  xlab("Episode length, log10") +
  ylab("Density")

p2 <- counts %>%
  ggplot(aes(x = log10(Length), color = Episode, fill = Episode)) +
  facet_grid(~Region) +
  geom_density(alpha = 0.25) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(strip.background = element_rect(fill = "white")) +
  theme(strip.text = element_text(colour = "black")) +
  xlab("Episode length, log10") +
  ylab("Density")

p3 <- counts %>%
  ggplot(aes(x = log10(Length), color = Episode, fill = Episode)) +
  facet_grid(~Layer) +
  geom_density(alpha = 0.25) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(strip.background = element_rect(fill = "white")) +
  theme(strip.text = element_text(colour = "black")) +
  xlab("Episode length, log10") +
  ylab("Density")

p4 <- counts %>%
  ggplot(aes(x = log10(Length), color = Episode, fill = Episode)) +
  facet_grid(~Cortex) +
  geom_density(alpha = 0.25) +
  theme_light(base_size = 8) +
  theme(legend.position = "top") +
  theme(strip.background = element_rect(fill = "white")) +
  theme(strip.text = element_text(colour = "black")) +
  xlab("Episode length, log10") +
  ylab("Density")

ggarrange(
  ggarrange(p1, p2, widths = c(0.3, 0.7), labels = letters[ 1:2 ], font.label = list(size = 10), common.legend = TRUE),
  ggarrange(p3, p4, labels = letters[ 3:4 ], font.label = list(size = 10), legend = FALSE),
  nrow = 2,
  heights = c(0.55, 0.45)
)
```

**Figure 4.** Episode length distribution in movement and rest in all samples **(a)**
and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.

## Average membrane potential {.unlisted .unnumbered}

```{r, include = TRUE, warning = FALSE, message = FALSE, fig.height = 5.4}
plot_statistics_fit(
  data = stats,
  variable = "Mean",
  title = "Average membrane potential, mV"
)
```

**Figure 5.** Average membrane potential during movement and rest in all samples **(a)**
and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.

## Average membrane potential (no AP) {.unlisted .unnumbered}

```{r, include = TRUE, warning = FALSE, message = FALSE, fig.height = 5.4}
plot_statistics_fit(
  data = stats,
  variable = "MeanNoAP",
  title = "Average membrane potential, mV"
)
```

**Figure 6.** Average membrane potential (excluding episodes with AP) during movement and rest
in all samples **(a)** and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.


## Membrane potential variability {.unlisted .unnumbered}

```{r, include = TRUE, warning = FALSE, message = FALSE, fig.height = 5.4}
plot_statistics_fit(
  data = stats,
  variable = "SD",
  title = "Membrane potential variability, mV"
)
```

**Figure 7.** Membrane potential variability during movement and rest
in all samples **(a)** and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.


## Membrane potential variability (no AP) {.unlisted .unnumbered}

```{r, include = TRUE, warning = FALSE, message = FALSE, fig.height = 5.4}
plot_statistics_fit(
  data = stats,
  variable = "SDNoAP",
  title = "Membrane potential variability, mV"
)
```

**Figure 8.** Membrane potential variability (excluding episodes with AP) during movement and rest
in all samples **(a)** and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.


## Number of action potentials {.unlisted .unnumbered}

```{r, include = TRUE, warning = FALSE, message = FALSE, fig.height = 5.4}
plot_statistics_fit(
  data = stats,
  variable = "NumberOfAP",
  title = "Number of action potentials"
)
```

**Figure 9.** Number of action potentials fired during movement and rest
in all samples **(a)** and grouped by region **(b)**, layer **(c)**, and cortex **(d)**.
