```{r r_setup, include = FALSE}
# snakemake <- readRDS(".final_emg_episodes.Rmd.RDS")
snakemake@source("R/rmd_setup.R")
snakemake@source("R/getSampleFile.R")
library(data.table)
library(dplyr)
library(foreach)
library(ggplot2)
library(wesanderson)
library(ggpubr)
library(cowplot)

config <- snakemake@config

samples <- fread(snakemake@input$samples)
```

---
date: <small>`r Sys.Date()`</small>
author: <small>`r config$report$author`</small>
title: `r config$report$title`
---

# $V_m$ dynamics {.tabset .tabset-pills}

## Movement onset

The detected movement and rest episodes were filtered and only the episodes longer than 500 ms were kept for further
analysis. The movement episodes were also required to follow a rest period of at least 500 ms.

```{r}
all <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]

  movement <- fread(getSampleFile(snakemake@input$movement, sample[ , AnimalID ], sample[ , CellName ]))
  rest <- fread(getSampleFile(snakemake@input$rest, sample[ , AnimalID ], sample[ , CellName ]))

  rbind(movement, rest) %>%
    .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}

filter <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]

  movement <- fread(getSampleFile(snakemake@input$movement_filter_onset, sample[ , AnimalID ], sample[ , CellName ]))
  rest <- fread(getSampleFile(snakemake@input$rest_filter_onset, sample[ , AnimalID ], sample[ , CellName ]))

  rbind(movement, rest) %>%
    .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}
```

```{r, include = TRUE}
rbind(
  all[ Movement == TRUE, list(Count = .N, Type = "Before"), by = SID ],
  filter[ Movement == TRUE, list(Count = .N, Type = "After"), by = SID ]
) %>%
  .[ , Type := factor(Type, levels = c("Before", "After")) ] %>%
  ggplot() +
  geom_bar(aes(x = SID, y = Count, fill = Type), stat = "identity", position = "dodge") +
  theme_light(base_size = 8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab("") +
  theme(legend.position = "top") +
  theme(legend.title = element_blank())
```

**Figure 1.** Number of detected movement episodes before and after filtering.

```{r, include = TRUE}
rbind(
  all[ Movement == FALSE, list(Count = .N, Type = "Before"), by = SID ],
  filter[ Movement == FALSE, list(Count = .N, Type = "After"), by = SID ]
) %>%
  .[ , Type := factor(Type, levels = c("Before", "After")) ] %>%
  ggplot() +
  geom_bar(aes(x = SID, y = Count, fill = Type), stat = "identity", position = "dodge") +
  theme_light(base_size = 8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab("") +
  theme(legend.position = "top") +
  theme(legend.title = element_blank())
```

**Figure 2.** Number of detected rest episodes before and after filtering.

```{r, include = TRUE}
emg <- foreach(file = snakemake@input$onset_emg, .combine = rbind) %do% {
  data <- fread(file)
  x <- as.matrix(data[ 2:nrow(data), 2:ncol(data) ])
  rownames(x) <- data[ 2:nrow(data), V1 ]
  x
}

time <- data.table(Index = colnames(x)) %>%
  .[ , Time := seq(0, 1 - 1 / 20000, 1 / 20000) - 0.5 ] %>%
  .[ ]

emg <- emg %>%
  reshape2::melt() %>%
  setDT() %>%
  setnames(c("EventID", "Index", "EMG")) %>%
  merge(time) %>%
  .[ , list(EMG = mean(abs(EMG))), by = Time ] %>%
  .[ order(Time) ]

emg %>%
  ggplot() +
  geom_line(aes(x = Time, y = EMG), linewidth = 0.25) +
  geom_vline(aes(xintercept = 0), color = "orange") +
  theme_light(base_size = 8) +
  xlab("Time") +
  ylab("Average rectified EMG")
```

**Figure 3.** Average high-pass filtered (at 2Hz) rectified EMG data during the onset of movement episodes in all cells.

```{r, include = TRUE, fig.height = 5.8}
colors <- wes_palette("Zissou1")

time <- data.table(Index = colnames(x)) %>%
  .[ , Time := seq(0, 1 - 1 / 20000, 1 / 20000) - 0.5 ] %>%
  .[ ]

eventData <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  file <- getSampleFile(snakemake@input$onset_vm, sample[ , AnimalID ], sample[ , CellName ])
  data <- fread(file)
  x <- as.matrix(data[ 2:nrow(data), 2:ncol(data) ])
  rownames(x) <- data[ 2:nrow(data), V1 ]

  x %>%
    reshape2::melt() %>%
    setDT() %>%
    setnames(c("ID", "Index", "Vm")) %>%
    merge(time) %>%
    .[ , SID := sample[ , SID ] ] %>%
    .[ Time >= -0.4 & Time <= 0.4 ] %>%
    .[ Time >= -0.4 & Time <= -0.2, Type := "Baseline" ] %>%
    .[ Time >= -0.1 & Time <= 0, Type := "Pre-movement" ] %>%
    .[ Time > 0 & Time <= 0.2, Type := "Movement onset" ] %>%
    .[ Time > 0.2 & Time <= 0.4, Type := "Late movement" ] %>%
    .[ , Region := paste(sample[ , Cortex ], sample[ , Layer ]) ]
}

average_data <- eventData %>%
  .[ , list(Vm = mean(Vm)), by = list(Region, Time) ]

actionPotentials <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  ap <- getSampleFile(snakemake@input$action_potentials, sample[ , AnimalID ], sample[ , CellName ]) %>%
    fread() %>%
    .[ , ID := paste0("A", 1:.N) ]
  movement <- getSampleFile(snakemake@input$movement_filter_onset, sample[ , AnimalID ], sample[ , CellName ]) %>%
    fread() %>%
    .[ , Start := Start - 0.5 ]

  if (nrow(ap) == 0) {
    return(data.table())
  }

  setkeyv(ap, c("Start", "End"))
  setkeyv(movement, c("Start", "End"))

  foreach(channel = movement[ , unique(Channel) ], .combine = rbind) %do% {
    foverlaps(movement[ Channel == channel ], ap[ Channel == channel ])
  } %>%
    na.omit() %>%
    .[ , i.Start := i.Start + 0.5 ] %>%
    .[ , Time := Start - i.Start ] %>%
    .[ Time < 0.4 & Time > -0.4 ] %>%
    .[ , SID := sample[ , SID ] ] %>%
    .[ , Region := paste(sample[ , Cortex ], sample[ , Layer ]) ]
}

plot <- list()
for (region in c("S1 L23", "S1 L5", "M1 L23", "M1 L5")) {
  region_average <- average_data[ Region == region ]

  region_label <- gsub(x = region, pattern = "23", replacement = "2/3")

  max_vm <- region_average[ , max(Vm) ] + 0.5

  p1 <- region_average %>%
    ggplot() +
    annotate("rect", xmin = -0.4, xmax = -0.2, ymin = -Inf, ymax = Inf, fill = colors[ 1 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = -0.1, xmax = 0, ymin = -Inf, ymax = Inf, fill = colors[ 2 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0, xmax = 0.1, ymin = -Inf, ymax = Inf, fill = colors[ 3 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0.2, xmax = 0.4, ymin = -Inf, ymax = Inf, fill = colors[ 4 ], linewidth = 0.5, alpha = 0.5) +
    geom_line(aes(x = Time, y = Vm), color = colors[ 5 ], linewidth = 0.25) +
    theme_light(base_size = 8) +
    ylab("Membrane\npotential, V (mV)") +
    ggtitle(region_label) +
    theme(plot.title = element_text(hjust = 0.5, size = 9, face = "bold")) +
    scale_x_continuous(name = "Time, t (s)", breaks = c(-0.4, -0.2, 0, 0.2, 0.4), limits = c(-0.4, 0.4)) +
    annotate("text", x = -0.3, y = max_vm, label = "B", size = 2.5) +
    annotate("text", x = -0.05, y = max_vm, label = "P", size = 2.5) +
    annotate("text", x = 0.05, y = max_vm, label = "O", size = 2.5) +
    annotate("text", x = 0.3, y = max_vm, label = "L", size = 2.5)

  typeAverage <- eventData[ Region == region ] %>%
    .[ , list(Vm = mean(Vm)), by = list(SID, Type) ] %>%
    .[ Type != "None" ] %>%
    .[ Type == "Baseline", Type := "B" ] %>%
    .[ Type == "Pre-movement", Type := "P" ] %>%
    .[ Type == "Movement onset", Type := "O" ] %>%
    .[ Type == "Late movement", Type := "L" ] %>%
    .[ , Type := factor(Type, levels = c("B", "P", "O", "L")) ] %>%
    .[ , Animal := gsub(x = SID, pattern = "(W[0-9]).*", replacement = "\\1") ] %>%
    .[ , Animal := factor(Animal, levels = c("W1", "W2", "W3", "W4")) ]

  p2 <- typeAverage %>%
    ggpaired(x = "Type", y = "Vm", id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    geom_boxplot(aes(color = Type), outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(aes(x = Type, y = Vm, color = Type), alpha = 0.75, size = 0.75) +
    stat_compare_means(
      paired = TRUE,
      comparisons = list(c("B", "P"), c("P", "O"), c("B", "L")),
      method = "wilcox", size = 2.5) +
    stat_compare_means(
      paired = TRUE,
      comparisons = list(c("O", "L")),
      method = "wilcox", size = 2.5) +
    theme_light(base_size = 8) +
    theme(legend.position = "none") +
    ylab("Membrane potential, V (mV)") +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1))) +
    xlab("") +
    scale_colour_manual(values = c("B" = colors[ 1 ], "P" = colors[ 2 ], "O" = colors[ 3 ], "L" = colors[ 4 ]))

  p3 <- actionPotentials %>%
    .[ Region == region ] %>%
    ggplot() +
    annotate("rect", xmin = -0.4, xmax = -0.2, ymin = -Inf, ymax = Inf, fill = colors[ 1 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = -0.1, xmax = 0, ymin = -Inf, ymax = Inf, fill = colors[ 2 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0, xmax = 0.1, ymin = -Inf, ymax = Inf, fill = colors[ 3 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0.2, xmax = 0.4, ymin = -Inf, ymax = Inf, fill = colors[ 4 ], linewidth = 0.5, alpha = 0.5) +
    geom_histogram(aes(x = Time), fill = "white", color = "black", binwidth = 0.025) +
    theme_light(base_size = 8) +
    ylab("AP count") +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_x_continuous(name = "Time, t (s)", breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
    expand_limits(y = c(0, 70)) +
    annotate("text", x = -0.3, y = 69, label = "B", size = 2.5) +
    annotate("text", x = -0.05, y = 69, label = "P", size = 2.5) +
    annotate("text", x = 0.05, y = 69, label = "O", size = 2.5) +
    annotate("text", x = 0.3, y = 69, label = "L", size = 2.5)

  p5 <- ggdraw() +
    draw_plot(p1, 0, 0.7, 1, 0.3) +
    draw_plot(p2, 0.068, 0.25, 1 - 0.068, 0.45) +
    draw_plot(p3, 0.08, 0, 1 - 0.08, 0.25)

  # Only for the first in list
  if (region == "S1 L23") {
    p5 <- p5 + draw_plot_label(letters[ 1:3 ], x = c(0, 0, 0), y = c(1, 0.7, 0.25), size = 9)
  }

  plot[[region]] <- p5
}

ggarrange(plotlist = plot, ncol = 4)
```

**Figure 4.** Membrane potential and action potential dynamics during spontaneous movement
initiation. Four epochs of interest are highlighted (Baseline, B; Pre-movement, P; Movement
onset, O; and Late Movement, L). The zero time point marks the movement onset. **(a)** Grand
average membrane potential during movement onset in all regions of interest. **(b)** Average
membrane potential during each epoch in all regions of interest. The p-values were calculated
using the Wilcoxon signed-rank test for paired data. The points represent different cells, and
data of the same cell is connected by a line. **(c)** Peri-stimulus time histograms (PSTHs) of action
potential spikes in all regions of interest.


## Movement offset

The detected movement and rest episodes were filtered and only the episodes longer than 500 ms were kept for further
analysis. The movement episodes were also required to precede a rest period of at least 500 ms.

```{r}
all <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]

  movement <- fread(getSampleFile(snakemake@input$movement, sample[ , AnimalID ], sample[ , CellName ]))
  rest <- fread(getSampleFile(snakemake@input$rest, sample[ , AnimalID ], sample[ , CellName ]))

  rbind(movement, rest) %>%
    .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}

filter <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]

  movement <- fread(getSampleFile(snakemake@input$movement_filter_offset, sample[ , AnimalID ], sample[ , CellName ]))
  rest <- fread(getSampleFile(snakemake@input$rest_filter_offset, sample[ , AnimalID ], sample[ , CellName ]))

  rbind(movement, rest) %>%
    .[ , SID := paste(sample[ , AnimalID ], sample[ , CellName ], sep = "_") ]
}
```

```{r, include = TRUE}
rbind(
  all[ Movement == TRUE, list(Count = .N, Type = "Before"), by = SID ],
  filter[ Movement == TRUE, list(Count = .N, Type = "After"), by = SID ]
) %>%
  .[ , Type := factor(Type, levels = c("Before", "After")) ] %>%
  ggplot() +
  geom_bar(aes(x = SID, y = Count, fill = Type), stat = "identity", position = "dodge") +
  theme_light(base_size = 8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab("") +
  theme(legend.position = "top") +
  theme(legend.title = element_blank())
```

**Figure 1.** Number of detected movement episodes before and after filtering.

```{r, include = TRUE}
rbind(
  all[ Movement == FALSE, list(Count = .N, Type = "Before"), by = SID ],
  filter[ Movement == FALSE, list(Count = .N, Type = "After"), by = SID ]
) %>%
  .[ , Type := factor(Type, levels = c("Before", "After")) ] %>%
  ggplot() +
  geom_bar(aes(x = SID, y = Count, fill = Type), stat = "identity", position = "dodge") +
  theme_light(base_size = 8) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  xlab("") +
  theme(legend.position = "top") +
  theme(legend.title = element_blank())
```

**Figure 2.** Number of detected rest episodes before and after filtering.

```{r, include = TRUE}
emg <- foreach(file = snakemake@input$offset_emg, .combine = rbind) %do% {
  data <- fread(file)
  x <- as.matrix(data[ 2:nrow(data), 2:ncol(data) ])
  rownames(x) <- data[ 2:nrow(data), V1 ]
  x
}

time <- data.table(Index = colnames(x)) %>%
  .[ , Time := seq(0, 1 - 1 / 20000, 1 / 20000) - 0.5 ] %>%
  .[ ]

emg <- emg %>%
  reshape2::melt() %>%
  setDT() %>%
  setnames(c("EventID", "Index", "EMG")) %>%
  merge(time) %>%
  .[ , list(EMG = mean(abs(EMG))), by = Time ] %>%
  .[ order(Time) ]

emg %>%
  ggplot() +
  geom_line(aes(x = Time, y = EMG), linewidth = 0.25) +
  geom_vline(aes(xintercept = 0), color = "orange") +
  theme_light(base_size = 8) +
  xlab("Time") +
  ylab("Average rectified EMG")
```

**Figure 3.** Average high-pass filtered (at 2Hz) rectified EMG data during the onset of movement episodes in all cells.

```{r, include = TRUE, fig.height = 5.8}
colors <- wes_palette("Zissou1")

time <- data.table(Index = colnames(x)) %>%
  .[ , Time := seq(0, 1 - 1 / 20000, 1 / 20000) - 0.5 ] %>%
  .[ ]

eventData <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  file <- getSampleFile(snakemake@input$offset_vm, sample[ , AnimalID ], sample[ , CellName ])
  data <- fread(file)
  x <- as.matrix(data[ 2:nrow(data), 2:ncol(data) ])
  rownames(x) <- data[ 2:nrow(data), V1 ]

  x %>%
    reshape2::melt() %>%
    setDT() %>%
    setnames(c("ID", "Index", "Vm")) %>%
    merge(time) %>%
    .[ , SID := sample[ , SID ] ] %>%
    .[ Time >= -0.4 & Time <= 0.4 ] %>%
    .[ Time >= -0.4 & Time <= -0.2, Type := "Late movement" ] %>%
    .[ Time >= -0.1 & Time <= 0, Type := "Movement offset" ] %>%
    .[ Time > 0 & Time <= 0.2, Type := "Post-movement" ] %>%
    .[ Time > 0.2 & Time <= 0.4, Type := "Baseline" ] %>%
    .[ , Region := paste(sample[ , Cortex ], sample[ , Layer ]) ]
}

average_data <- eventData %>%
  .[ , list(Vm = mean(Vm)), by = list(Region, Time) ]

actionPotentials <- foreach(i = seq_len(nrow(samples)), .combine = rbind) %do% {
  sample <- samples[ i ]
  ap <- getSampleFile(snakemake@input$action_potentials, sample[ , AnimalID ], sample[ , CellName ]) %>%
    fread() %>%
    .[ , ID := paste0("A", 1:.N) ]
  movement <- getSampleFile(snakemake@input$movement_filter_offset, sample[ , AnimalID ], sample[ , CellName ]) %>%
    fread() %>%
    .[ , Start := Start - 0.5 ]

  if (nrow(ap) == 0) {
    return(data.table())
  }

  setkeyv(ap, c("Start", "End"))
  setkeyv(movement, c("Start", "End"))

  foreach(channel = movement[ , unique(Channel) ], .combine = rbind) %do% {
    foverlaps(movement[ Channel == channel ], ap[ Channel == channel ])
  } %>%
    na.omit() %>%
    .[ , i.Start := i.Start + 0.5 ] %>%
    .[ , Time := Start - i.Start ] %>%
    .[ Time < 0.4 & Time > -0.4 ] %>%
    .[ , SID := sample[ , SID ] ] %>%
    .[ , Region := paste(sample[ , Cortex ], sample[ , Layer ]) ]
}

plot <- list()
for (region in c("S1 L23", "S1 L5", "M1 L23", "M1 L5")) {
  region_average <- average_data[ Region == region ]

  region_label <- gsub(x = region, pattern = "23", replacement = "2/3")

  max_vm <- region_average[ , max(Vm) ] + 0.5

  p1 <- region_average %>%
    ggplot() +
    annotate("rect", xmin = -0.4, xmax = -0.2, ymin = -Inf, ymax = Inf, fill = colors[ 1 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = -0.1, xmax = 0, ymin = -Inf, ymax = Inf, fill = colors[ 2 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0, xmax = 0.1, ymin = -Inf, ymax = Inf, fill = colors[ 3 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0.2, xmax = 0.4, ymin = -Inf, ymax = Inf, fill = colors[ 4 ], linewidth = 0.5, alpha = 0.5) +
    geom_line(aes(x = Time, y = Vm), color = colors[ 5 ], linewidth = 0.25) +
    theme_light(base_size = 8) +
    ylab("Membrane\npotential, V (mV)") +
    ggtitle(region_label) +
    theme(plot.title = element_text(hjust = 0.5, size = 9, face = "bold")) +
    scale_x_continuous(name = "Time, t (s)", breaks = c(-0.4, -0.2, 0, 0.2, 0.4), limits = c(-0.4, 0.4)) +
    annotate("text", x = -0.3, y = max_vm, label = "L", size = 2.5) +
    annotate("text", x = -0.05, y = max_vm, label = "O", size = 2.5) +
    annotate("text", x = 0.05, y = max_vm, label = "P", size = 2.5) +
    annotate("text", x = 0.3, y = max_vm, label = "B", size = 2.5)

  typeAverage <- eventData[ Region == region ] %>%
    .[ , list(Vm = mean(Vm)), by = list(SID, Type) ] %>%
    .[ Type != "None" ] %>%
    .[ Type == "Late movement", Type := "L" ] %>%
    .[ Type == "Movement offset", Type := "O" ] %>%
    .[ Type == "Post-movement", Type := "P" ] %>%
    .[ Type == "Baseline", Type := "B" ] %>%
    .[ , Type := factor(Type, levels = c("L", "O", "P", "B")) ] %>%
    .[ , Animal := gsub(x = SID, pattern = "(W[0-9]).*", replacement = "\\1") ] %>%
    .[ , Animal := factor(Animal, levels = c("W1", "W2", "W3", "W4")) ]

  p2 <- typeAverage %>%
    ggpaired(x = "Type", y = "Vm", id = "SID",
             line.color = "gray", line.size = 0.2, point.size = 0, color = "white") +
    geom_boxplot(aes(color = Type), outlier.alpha = 0, fill = NA, linewidth = 0.25) +
    geom_point(aes(x = Type, y = Vm, color = Type), alpha = 0.75, size = 0.75) +
    stat_compare_means(
      paired = TRUE,
      comparisons = list(c("L", "O"), c("O", "P"), c("L", "B")),
      method = "wilcox", size = 2.5) +
    stat_compare_means(
      paired = TRUE,
      comparisons = list(c("P", "B")),
      method = "wilcox", size = 2.5) +
    theme_light(base_size = 8) +
    theme(legend.position = "none") +
    ylab("Membrane potential, V (mV)") +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1))) +
    xlab("") +
    scale_colour_manual(values = c("L" = colors[ 1 ], "O" = colors[ 2 ], "P" = colors[ 3 ], "B" = colors[ 4 ]))

  p3 <- actionPotentials %>%
    .[ Region == region ] %>%
    ggplot() +
    annotate("rect", xmin = -0.4, xmax = -0.2, ymin = -Inf, ymax = Inf, fill = colors[ 1 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = -0.1, xmax = 0, ymin = -Inf, ymax = Inf, fill = colors[ 2 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0, xmax = 0.1, ymin = -Inf, ymax = Inf, fill = colors[ 3 ], linewidth = 0.5, alpha = 0.5) +
    annotate("rect", xmin = 0.2, xmax = 0.4, ymin = -Inf, ymax = Inf, fill = colors[ 4 ], linewidth = 0.5, alpha = 0.5) +
    geom_histogram(aes(x = Time), fill = "white", color = "black", binwidth = 0.025) +
    theme_light(base_size = 8) +
    ylab("AP count") +
    theme(strip.background = element_rect(fill = "white")) +
    theme(strip.text = element_text(colour = "black")) +
    scale_x_continuous(name = "Time, t (s)", breaks = c(-0.4, -0.2, 0, 0.2, 0.4)) +
    expand_limits(y = c(0, 70)) +
    annotate("text", x = -0.3, y = 69, label = "L", size = 2.5) +
    annotate("text", x = -0.05, y = 69, label = "O", size = 2.5) +
    annotate("text", x = 0.05, y = 69, label = "P", size = 2.5) +
    annotate("text", x = 0.3, y = 69, label = "B", size = 2.5)

  p5 <- ggdraw() +
    draw_plot(p1, 0, 0.7, 1, 0.3) +
    draw_plot(p2, 0.068, 0.25, 1 - 0.068, 0.45) +
    draw_plot(p3, 0.08, 0, 1 - 0.08, 0.25)

  # Only for the first in list
  if (region == "S1 L23") {
    p5 <- p5 + draw_plot_label(letters[ 1:3 ], x = c(0, 0, 0), y = c(1, 0.7, 0.25), size = 9)
  }

  plot[[region]] <- p5
}

ggarrange(plotlist = plot, ncol = 4)
```

**Figure 4.** Membrane potential and action potential dynamics during spontaneous movement
initiation. Four epochs of interest are highlighted (Late Movement, L; Movement offset, O;
Post-movement, P; and Baseline, B). The zero time point marks the movement onset. **(a)** Grand
average membrane potential during movement onset in all regions of interest. **(b)** Average
membrane potential during each epoch in all regions of interest. The p-values were calculated
using the Wilcoxon signed-rank test for paired data. The points represent different cells, and
data of the same cell is connected by a line. **(c)** Peri-stimulus time histograms (PSTHs) of action
potential spikes in all regions of interest.
