## `r animalId` `r cellName` {.unlisted .unnumbered}

```{r}
data <- fread(getSampleFile(snakemake@input$vm_filter, animalId, cellName))
x <- as.matrix(data[ 2:nrow(data), 2:ncol(data) ])
rownames(x) <- data[ 2:nrow(data), V1 ]
time <- data.table(Index = colnames(data)[ 2:ncol(data) ]) %>%
  .[ , Time := seq(0, 10, 1 / 20000) ] %>%
  .[ ]

vmData <- x %>%
  reshape2::melt() %>%
  as.data.table() %>%
  setnames(c("Trial", "Index", "Value")) %>%
  merge(time, by = "Index") %>%
  .[ , Trial := factor(Trial, levels = data[ 2:nrow(data), V1 ]) ]

aps <- fread(getSampleFile(snakemake@input$action_potentials, animalId, cellName)) %>%
  .[ , Trial := levels(vmData[ , Trial ])[ Channel + 1 ] ] %>%
  .[ , ID := make.names(1:.N) ]

apData <- foreach(i = seq_len(nrow(aps)), .combine = rbind) %do% {
  ap <- aps[ i ]
  vmData[ Trial == ap[ , Trial ] ] %>%
    .[ Time >= ap[ , Start ] ] %>%
    .[ Time <= ap[ , End ] ] %>%
    .[ , ID := ap[ , ID ] ]
}
```

The Vm data were not filtered nor centered.

Action potentials (APs) were detected using the first derivative of the membrane potential, $V_m'$. The onset
of the AP was defined as the time point where $V_m'$ exceeded 22 mV/ms. The offset of the AP was defined as
the time point 2 ms after the AP peak ($V_m' = 0$ mV/ms). '

```{r, include = TRUE, fig.height = vmData[ , length(unique(Trial))] * 0.3 + 0.1}
p <- vmData %>%
  ggplot() +
  facet_wrap(~Trial, ncol = 1) +
  geom_line(aes(x = Time, y = Value), linewidth = 0.05) +
  theme_light(base_size = 8) +
  scale_x_continuous(limits = c(0, 10), expand = c(0, 0)) +
  theme(panel.spacing = unit(0, "lines")) +
  theme(strip.background = element_blank()) +
  theme(strip.text.x = element_blank()) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.text.y = element_blank()) +
  theme(axis.ticks.y = element_blank()) +
  ylab("")

# Only if there are detected action potentials
if (nrow(aps) != 0) {
  p <- p + geom_line(data = apData, aes(x = Time, y = Value, group = ID), linewidth = 0.25, color = "red")
}

p
```

**Figure 1.** Membrane potential in animal `r animalId` cell `r cellName`. Detected action potentials
are marked in red.

```{r, include = TRUE, fig.height = 2.2}
vmData %>%
  .[ , Channel := as.numeric(Trial) ] %>%
  .[ , Time := Time + 10 * (Channel - 1) ] %>%
  ggplot() +
  geom_line(aes(x = Time, y = Value), linewidth = 0.05) +
  theme_light(base_size = 8) +
  ylab("Membrane potential, mV") +
  xlab("Time, s")
```

**Figure 2.** Continuous membrane potential data through all the trials.
